Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-24 paper.tex
edits to algo section

We have $N$ arms. Arm $i$ has a fixed but unknown attribute vector $u_i\in \mathbb{R}^{m}$.

A stream of myopic selfish agents come to our system.  Agent $t$ has linear preferences over attributes described by a vector $\theta_t \in \mathbb{R}^m$ that is unknown to the principal and drawn i.i.d. from a known distribution $F(\cdot)$. We refer synonomously to an agent and that agent's preference vector: when we say ``an agent $\theta$'', we mean ``an agent with preference vector $\theta$.''

@@

To support later development, we define three additional pieces of notation.
We let $B(\theta)$ and $\hat{B}(\theta)$ refer to the index of the arm that is best and second best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$ and $\hat{B}(\theta)=\argmax_{i\neq B(\theta)}\theta\cdot u_{i}$, breaking ties uniformly at random. We let $N(i,t)$ denote the cardinality of $A_t$, i.e., the number of pulls of arm $i$ at times up to and including $t$.

\section{Upper Bound}
\label{sec:ub}

@@

\subsection{Our Algorithm}
Before we introduce our algorithm, we need to use the following definition:

\begin{definition}
We call time $t_{n}$ as the starting point of the $n^{th}$ round if $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$. We call the time period from $t_{n}$ to $t_{n+1}$ as the $n^{th}$ round.
\end{definition}

We consider an algorithm that offers incentive to an arm $i$ if and only if both of the following criterias are met:
\begin{itemize}
\item the myopic probability of pulling arm $i$ is low; 
\item arm $i$ has not been played or incentivized before in this round.
\end{itemize}
We break ties randomly. If we decides to incentivize an arm, we use ``pay whatever it takes'' strategy (We use ``pay whatever it takes'' strategy mainly because of its simplicity. In Section~\ref{sec:pi}, we provide a more realistic algorithm which has the same payment budget bound and regret bound). This algorithm does not need to know $T$ in advance. The detailed algorithm is as follows:

\begin{algorithm}
\caption{Algorithm: Incentivizing Exploration}
\label{Alg1}
\begin{algorithmic}
\STATE Set n = 1 to denote the round number;
\FOR{ $t = 1, 2, 3, \cdots$}{
	\IF{the myopic probability of pulling an arm is less than $n^{-1}$ and no agents have pulled that arm in this round (break ties randomly)}
	\STATE{ we pay whatever it takes to incentivize that arm}\ELSE 
		\STATE {let the agents play myopically}\ENDIF
		\STATE $n = min_{i} N(i,t)$
}\ENDFOR

@@

\subsection{Assumptions}
In this secion, we discuss several assumptions that we need to acheive our results. Throughout this paper, we use $F(\cdot)$ to denote the agent's preference distribution, which could either be a continuous distribution or a discrete distribution. Denote

@@

\begin{assumption}
Denote $p=\min_{i}P(\{\theta: B(\theta)=i\})$. Throughout this paper, we assume $p>0$.
\label{A3}
\end{assumption}

>>>>

We have $N$ arms. Arm $i$ has a fixed but unknown attribute vector $u_i\in \mathbb{R}^{m}$. 
A stream of myopic selfish agents come to our system.  Agent $t$ has linear preferences over attributes described by a vector $\theta_t \in \mathbb{R}^m$ that is unknown to the principal and drawn i.i.d. from a known distribution $F(\cdot)$ with compact support. We refer synonomously to an agent and that agent's preference vector: when we say ``an agent $\theta$'', we mean ``an agent with preference vector $\theta$.''

@@

To support later development, we define some additional notation.
We let $B(\theta)$ and $\hat{B}(\theta)$ refer to the index of the arm that is best and second best for an agent with preference vector $\theta$, $B(\theta) \in \argmax_i \theta \cdot u_i$ and $\hat{B}(\theta)=\argmax_{i\neq B(\theta)}\theta\cdot u_{i}$, breaking ties uniformly at random. We let $N(i,t)$ denote the cardinality of $A_t$, i.e., the number of pulls of arm $i$ at times up to and including $t$.
We call time $t_{n}=\min_{t}\{\forall i, N(i,t)\geq n\}$ the {\it starting point of the $n^{th}$ round}. We call the set of times $[t_{n}, t_{n+1})$ the {\it $n^{th}$ round}.

\section{Algorithm and Upper Bound}
\label{sec:ub}

@@

\subsection{Our Algorithm}
Our algorithm incentivizes pulling an arm $i$ at a time $t$ in round $n$ if and only if both of the following criteria are met:
\begin{itemize}
\item the probability of pulling arm $i$ would be below $n^{-1}$ without incentives; 
\item arm $i$ has not been played previously in the current round.
\end{itemize}
Ties are broken randomly.  This algorithm does not need to know the horizon $T$ in advance.

If our algorithm decides to incentivize an arm $i$, it uses the ``pay whatever it takes'' strategy in which the payment offered is $\max_{\theta,j} \theta \cdot (u_j - u_i)$. This maximum over $\theta$ is taken over the support of $F$, which we recall is assumed compact.  (We use this ``pay whatever it takes'' strategy for its simplicity, and in Section~\ref{sec:pi} we provide an alternate and smaller incentive payment that achieves the same payment budget bound and regret bound).

We describe our algorithm in detail as follows:

\begin{algorithm}
\caption{Algorithm: Incentivizing Exploration}
\label{Alg1}
\begin{algorithmic}
\STATE Set n = 1 to denote the round number;
\FOR{ $t = 1, 2, 3, \cdots$}{
	\STATE Let $S = \{ i : P( \theta \cdot u_{i,t} > \theta \cdot u_{j,t}\ \forall j\ne i | u_{j,t}\ \forall j) < n^{-1}\}$ be the set of arms with unincentivized probability of being pulled below $n^{-1}$.
  \IF {$S$ is non-empty}
    \STATE{Choose an arm $i$ uniformly at random from $S$}
    \STATE{Pay whatever it takes to incentivize pulling arm $i$, i.e., offer payment 
    $c_{i,t} = \max_{\theta,j} \theta \cdot (u_{j,t} - u_{i,t})$ and $c_{j,t} = 0$ for $j \ne i$.}
  \ELSE
  \STATE {Let agents play myopically, i.e., offer payment $c_{j,t} = 0$ for all $j$}
  \ENDIF
  \STATE Update $u_{i,t}$ and $N(i,t)$ for the pulled arm
  \STATE Update the round number, $n = \min_{i} N(i,t)$
}\ENDFOR

@@

\subsection{Assumptions}
In this secion, we discuss several assumptions that we need to acheive our results.  Denote

@@

\begin{assumption}
Denote $p=\min_{i}P(\{\theta: B(\theta)=i\})$. We assume $p>0$.
\label{A3}
\end{assumption}
